Word Sense Disambiguation\\ \small{Leveraging the NLTK Toolkit and External Tools}

### 2011-04-14 paper/paper.tex

We wrote our main control program, classify.py, so that it can choose either
Naive Bayes or Decision Trees classifier and any 
combination of  features. On top of this we wrote bash scripts that automated
looping through every combination of classifiers and features, along with
porting the results directly into the scorer.  Classify.py includes a help
switch -h, that explains the switches that control the different classifiers
and features along with any additional parameters that a certain feature might
support (for example, collocation has a window size parameter which defaults to
0) Performance was excellent for most of the features, allowing us to typically
run all of the words in the test set through every combination a classifier and
feature set in under an hour. (The number of runs can get quite high when you
factor in several parameters per feature, not just on/off)

@@

@@

%We're using this now, just on a different corpus, right?
%\subsubsection{Bootstrapping on the Brown Corpus}

\subsection{Looking through Different Corpora}

%The instances of the target words in the Brown corpus were very few, e.g., activate appeared only 3 times, and bootstrapping didn't seem to be very accurate in general.

>>>>

We wrote our main control program, classify.py, so that it can choose either
[we're just doing nb and decision trees now right?] classifier and any
combination of  features. On top of this we wrote bash scripts that automated
looping through every combination of classifiers and features, along with
porting the results directly into the scorer.  Classify.py includes a help
switch -h, that explains the switches that control the different classifiers
and features along with any additional parameters that a certain feature might
support (for example, collocation has a window size parameter which defaults to
0) Performance was excellent for most of the features, allowing us to typically
run all of the words in the test set through every combination a classifier and
feature set in under an hour. (The number of runs can get quite high when you
factor in several parameters per feature, not just on/off)

@@

\section{Looking through Different Corpora}

@@

%We're using this now, just on a different corpus, right?
%\subsubsection{Bootstrapping on the Brown Corpus} 
%The instances of the target words in the Brown corpus were very few, e.g., activate appeared only 3 times, and bootstrapping didn't seem to be very accurate in general.
